Data merging for WHO presentation

### 2020-10-26 PANNEURO_CFS_merge_script_WHO-pres.Rmd
Added BMI data to merge script

---
title: "PANCHANGE_data_merging"
author: "Christopher Huebel"
date: "17/08/2020"
output: html_document
---

@@

@@

```{r merge data frames}
dat <- left_join(
  coping_baseline,
  cfs_wave6, by = c("Sample", "ID")
)
```

>>>>

---
title: "Data merging for WHO presentation"
author: "Christopher Huebel and Molly Davies"
date: "17/08/2020"
output: html_document
---

@@

bmi_data <- read_rds(path = paste0(data_path, "/bmi.rds"))

@@

```{r rename NBR cohort in bmi dataset}
bmi_data <- bmi_data%>%
  mutate(
    Sample = 
    recode(
      Sample, 
      "SP0068" = "NBR"
    )
  )
```

```{r merge data frames}
dat1 <- left_join(
  coping_baseline,
  cfs_wave6, by = c("Sample", "ID")
)

dat <- left_join(
  dat1,
  bmi_data,
  by = c("Sample", "ID")
)
